Dummy classifier

### 2020-12-02 src/dummy_classifier.Rmd
Added plot of logistic regression

---
title: "Dummy classifier"
author: "Jarkko Toivonen"
date: "11/4/2020"
output: md_document
---

@@

library(tidyverse)
source("economic_effect_functions.R")
source('../../Hb_predictor_container/src/validate_stan_fit.R', chdir=T)
```

@@

dummy_predictor2 <- function(train, validate) {  # real logistic regression
  glm.fit <- glm(Hb_deferral ~ previous_Hb,
               data = train,
               family = binomial)

  print(glm.fit)

@@

  return(result)  
}

# get_metrics <- function(df, previous_Hb_threshold) {
#   df <- df %>% mutate(predicted_Hb_deferral=factor(ifelse(previous_Hb < previous_Hb_threshold, "Deferred", "Accepted"), levels=c("Accepted", "Deferred")))
#   
#   cm <- confusionMatrix(reference = df$Hb_deferral, data = df$predicted_Hb_deferral, positive = "Deferred", mode = "everything")
#   f1 <- cm$byClass["F1"]
#          #Sensitivity  = TPR
#   TPR <- cm$byClass['Sensitivity']
#   FPR <- 1 - cm$byClass['Specificity']
#   temp <- get_cost(TPR, FPR, TPR, FPR, p = parameters) # The parameters are from file economic_effect_functions.R
#   E6  <- temp$E6
#   E12 <- temp$E12
#   return(tibble(previous_Hb_threshold=previous_Hb_threshold, f1=f1, E6=E6, E12=E12))
# }
# 
# optimize_threshold <- function(df) {
#   thresholds <- seq(120, 150, by=2)
#   result <- map_dfr(thresholds, function(t) get_metrics(df, t))
#   
#   threshold <- result %>%
#     slice_max(f1) %>%
#     pull(previous_Hb_threshold)
#   return(list(threshold=threshold, result=result))
# }

@@

```{r}
# res_female <- optimize_threshold(train_female)
# res_male <- optimize_threshold(train_male)
```

Optimized thresholds on previous Hb for females and males
```{r}
# female_previous_Hb_threshold <- res_female$threshold
# male_previous_Hb_threshold <- res_male$threshold
# female_previous_Hb_threshold
# male_previous_Hb_threshold
```

```{r}
# res_female$result
# res_male$result
```

Final result on validate data
```{r}

# f1_female <- get_f1(validate_female, female_previous_Hb_threshold)
# f1_female
```

```{r}

# f1_male <- get_f1(validate_male, male_previous_Hb_threshold)
# f1_male
```

```{r}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  prediction_female <- dummy_predictor2(train_female, test_female)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor2(train_male, test_male)
} else {
  prediction_female <- dummy_predictor(validate_female, 125)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor(validate_male, 135)
}
head(prediction_female)
head(prediction_male)
```

```{r}
save(prediction_female, file="~/FRCBS/interval-sims/progesa-validate-female-dummy2.rdata")
save(prediction_male, file="~/FRCBS/interval-sims/progesa-validate-male-dummy2.rdata")
```

```{r}
dummy_result <- process_all_data(dummy2_ids, replicates=100)
```

@@

df
```

@@

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```
```{r}
roc_female
pr_female
roc_male
pr_male
```

```{r}
# v <- c(roc_female$roc$ci[c(2,1,3)], pr_female$ci[c(1,2,3)], 
#        roc_male$roc$ci[c(2,1,3)], pr_male$ci[c(1,2,3)])
# aucs <- as_tibble(matrix(v, ncol=6, byrow=TRUE))
# colnames(aucs) <- c("AUROC", "AUROC low", "AUROC high", "AUPR value", "AUPR low", "AUPR high")
# aucs <- aucs %>% 
#   mutate(Id=dummy2_ids) %>%
#   select(Id, everything())
# 
# aucs
```

```{r}
# dummy_result <- inner_join(aucs, dummy_result, by="Id")
# dummy_result
```

>>>>

---
title: "Dummy classifier"
author: "Jarkko Toivonen"
date: "11/4/2020"
output: 
  html_document: default
  md_document: default
---

@@

library(tidyverse)
library(knitr)
source("economic_effect_functions.R")
source('../../Hb_predictor_container/src/validate_stan_fit.R', chdir=T)
```

@@

logistic_regression <- function(train) {
  glm.fit <- glm(Hb_deferral ~ previous_Hb,
               data = train,
               family = binomial)
  return(glm.fit)  
}

dummy_predictor2 <- function(train, validate) {  # real logistic regression
  glm.fit <- logistic_regression(train)
  print(glm.fit)

@@

  return(list(result=result, fit=glm.fit))  
}

@@

```{r}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  res <- dummy_predictor2(train_female, test_female)
  prediction_female <- res$result
  fit_female <- res$fit

  res <- dummy_predictor2(train_male, test_male)
  prediction_male <- res$result
  fit_male <- res$fit
} else {
  prediction_female <- dummy_predictor(validate_female, 125)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor(validate_male, 135)
}
head(prediction_female)
head(prediction_male)
fit_male
fit_female
```

```{r}
if (FALSE) {
  save(prediction_female, file="~/FRCBS/interval-sims/progesa-validate-female-dummy2.rdata")
  save(prediction_male, file="~/FRCBS/interval-sims/progesa-validate-male-dummy2.rdata")
}
```

```{r}
dummy_result <- suppressMessages(process_all_data(dummy2_ids, replicates=100))
```

@@

kable(df)
```

```{r}
data <- tibble(previous_Hb = seq(100, 200))
data[["male"]] <- predict(fit_male, newdata=data, type="response")
data[["female"]] <- predict(fit_female, newdata=data, type="response")
data2 <- data %>% pivot_longer(cols=c(male, female), names_to="Sex", values_to="Probability")
#data2

mt <- df %>% filter(Id=="progesa-male-dummy") %>% select(threshold6, threshold12) %>% as.numeric()   # male thresholds
ft <- df %>% filter(Id=="progesa-female-dummy") %>% select(threshold6, threshold12) %>% as.numeric() # female thresholds
mhb <- approx(x = data$male,   y = data$previous_Hb, xout=mt)$y                                          # corresponding male hemoglobins
fhb <- approx(x = data$female, y = data$previous_Hb, xout=ft)$y                                          # corresponding female hemoglobins
threshold_data <- tibble(previous_Hb = c(mhb, fhb), Probability=c(mt, ft), text=c("t6", "t12", "t6", "t12"), Sex=c("male", "male", "female", "female"))
kable(threshold_data)

g <- data2 %>% ggplot(aes(x=previous_Hb, y=Probability, color=Sex)) + 
  geom_line() +
  geom_vline(data=threshold_data, mapping=aes(xintercept=previous_Hb, colour=Sex)) +
  geom_text(data=threshold_data, mapping=aes(x=previous_Hb, label=text), y=0.1, show.legend=FALSE, nudge_x=2.5)
g
```

@@

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```
```{r}
roc_female
pr_female$pr_plot
roc_male
pr_male$pr_plot
```
